---
title: "Homework 2"
author: "Raul Bassi"
date: "17/03/2020"
output: pdf_document
---

#Homework 2
(now done at home fr)

##BASIC R OPERATIONS

1.1)

```{r}
6 + 25
sqrt(sqrt(81) + sqrt(100))
54*645 - 1000/ 46
```

The computation is easy, I only chose whatever number and typed different combinations such as "6 + 25", "sqrt(sqrt(81) + sqrt(100))" and 54*645 - 1000/46". I am not able to explain why I did this way because i just randomly decided what i was gonna write.

```{r}
install.packages("devtools")
library(devtools)
install_github("tidyverse/ggplot2")
library(tidyverse)
help("separate")
```

I did not know if I was supposed to write the steps from 1.2 to 1.4 here so I wrote it anyway.

Just looked in Stackoverflow and found out how to create a pie chart!!!

library(ggplot2)
ggplot(df1, aes(x = 1, y = count, fill = berth_day))+
    geom_col(position = 'stack', 
             show.legend = F) +
    geom_text(aes(label = paste(berth_day, ': ', count)), 
               position = position_stack(vjust = .5)) +
    coord_polar(theta = "y") +
    theme_void()

Not gonna lie, I do not know what many of those things do but you said for me to find out so...

```{r}
apropos("test")
```

51, that is the year Palmeiras won their World championship!!


1.7) https://pt.stackoverflow.com/questions/260185/como-mudar-o-tipo-de-letra-em-um-gr%C3%A1fico-no-r

The question is about changing the font style in a plot using ggplot2. The answer says to add after ggplot, geom_"something" and labs, theme(plot.title = element_text(family = "selected font-style"))

1.8) If i were to install "my_package", I would use the function: install.packages("my_package") and to view it: library(my_package)

1.9) To understand how to use "my_function" I would type  help("my_function") in R. Outside R I would just use Stackoverflow.

1.10)
```{r}
vectorA <- c(1, 2, 3)
```

It creates a vector and classifies it as "num" in values session.

1.11)
```{r}
vectorB <- c('1','2','3')
```
It creates another vector and classifies it as "chr" in values session.

1.12)
```{r}
x <- c(1,2,3)
y <- c('1','2','3')
c(x,y)
```

When we combine, we combine. c(x,y) just combine both vectors into a single one

```{r}
mtcars
mean(mtcars$mpg)
median(mtcars$mpg)
```
Summarizing the median of the mpg in the data set is 19.2, while the mean is 20.09


1.14) Table

```{r}
table(mtcars$mpg)
```

1.15) All the articles expose mistakes in graphs. They could be bad lebeling the axes, lack of data, bad comparisons, pie charts that sum is more than 100% and many others.

1.16)
• The chance that it will rain tomorrow. (continuous quantitative)
• Numbers of cars that travel, in one day, on the busiest avenue in the city. (discrete quantitative)
• Customer satisfaction with the service: excellent, good, regular, bad, or very bad. (ordinal qualitative)
• Blood type. (nominal qualitative)
• Email of Company X customers. (nominal qualitative)
• Time of professional experience of employees of Company X, in years. (continuous quantitative)
• Time of professional experience of employees of Company X, in seconds. (discrete quantitative)
• Professional experience of Company X employees: high experience, medium experience, or low experience. (ordinal qualitative)
• Gender of the interviewee. (nominal qualitative)
• HDI of the countries. (continuous quantitative)
• The inflation rate for the year. (continuous quantitative)


## FIX THE CODE

2.1)
```{r}
2 + 2
```
without the "".

2.2)
```{r}
2 + pi
```
without the ""(again).

2.3)
```{r}
A = TRUE
```
Numbers cannot be TRUE or FALSE.

2.4)
```{r}
4/3
```
the bar is / not \.

2.5)
```{r}
help("cor.test")
```
CAPITAL LETTERS make a difference in R, and use "" in function help.

2.6)
```{r}
?cor.test
```
one ? does the work!!

2.7)
```{r}
help("if")
```
function help needs "" inside the ()

2.8)
```{r}
help("cor.test")
```
or help or ?, do not be indecise

2.9)
```{r}
#this is my sum
1 + 2
```
'#' to create a title not to make a sum.

2.10)
```{r}
numbers <- c(1, 2, 3, 4)
```
comma is necessary inbetween terms.

2.11)
```{r}
animals <- c("dog", "cat", "parrot", "bunny")
```
COMMA!!!!!!!!!!!!!!

2.12)
```{r}
animals <- C("dog", "cat", "parrot", "bunny")
```
CAPITAL LETTERS make a difference!!!!!!!!!!!!!!

2.13)
```{r}
head(mtcars)
```
I am tired of correcting typos of CAPITAL LETTERS.

2.14)
```{r}
str(mtcars)
```
I won't say again.

2.15)
```{r}
dim(mtcars)
```
Use () in this case, not []

2.16)
```{r}
names(mtcars)
```
names not nomes.

2.17)
```{r}
head(mtcars, n =10)
```
n instead of x

2.18)
```{r}
animals <- c("dog", "cat", "parrot", "bunny")
numbers <- c(1,2,3,4)
dat <- data.frame(animals,numbers)
```
4 variables, then 4 numbers.

2.19)
```{r}
dat <- c(1:100)
save(dat, file = "my_data.RData")
```
First the data, then the file.

2.20)
```{r}
data("diamonds")
ggplot(data = diamonds) +
geom_bar(mapping = aes(x = cut))
```
data have to have the data name written and aes function goes along with mapping in the geom_bar.

2.21)
```{r}
data("diamonds")
ggplot(data = diamonds) +
geom_bar(mapping = aes(y = cut))
```
geom_bar can only have one variable axis, or x or y.

2.22)
```{r}
p1 <- ggplot(data = diamonds) +
geom_bar(mapping = aes(x = cut))
p1 + theme_bw()
```
The theme needs to go after the plot code.

2.23)
```{r}
ggplot(data = diamonds) +
geom_bar(mapping = aes(x = cut), color = "red")
```
At this point I am tired of pointing the errors, but here is the parenthesis location.

##CHALLENGE
3.1)
```{r}
vr <- c(1:1000000)
Evr <- vr[lapply(x,"%%",2) == 0]
```

